### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

\subsection{Performance}
The second limitation of the current side-channel detection tool is the performance bottleneck, especially for those tools based on the symbolic analysis. For example, CaSym can only analyze small programs. CacheD perfroms better. However, it still can not handle large programs like RSA directly. It uses some domain knowledge to analyze only part of the program. The expensive cost comes from the symbolic execution. Symbolic execution can be used to explore all the possible paths, which is useful for many tasks. But it is significantly less likely for cache side channels bugs in crypto primitives. Cryptography primitives are more likely to have an even coverage of different paths (based on pseudo-random cipher states), and a branch-based side channel is vulnerable from the very first branch on secret data, making complex path conditions less often relevant.

@@

>>>>

\subsection{Performance}
The second limitation of the current side-channel detection tool is the performance bottleneck, especially for those tools based on the symbolic analysis. For example, CaSym can only analyze small programs. CacheD perfroms better. However, it still can not handle large programs like RSA directly. It uses some domain knowledge to analyze only part of the program. The expensive cost comes from the symbolic execution. Symbolic execution can be used to explore all the possible paths, which is useful for many tasks. But it is significantly less likely for cache side channels bugs in crypto primitives. Cryptography primitives are more likely to have an even coverage of different paths (based on pseudo-random cipher states), and a branch-based side channel is vulnerable from the very first branch on secret data, making complex path conditions less often relevant. Therefore, we choose to analyze a trace instead of the whole path. Another bottleneck is that the IR. While the IR can significantly decrease the difficulty of the implementation, it also gives introduce an average of 10x of the overall overhead. Third, using SMT solving can be convenient because of its generality, and it is commonly used for its precision when checking branch feasibility in symbolic execution. But the decision problems that an SMT solver handles are typically at least NP-hard. On the other hand, we can use some methods to avoid the solver and find side-channel leakages in a more efficient way.

@@

In the section, we give necessary definitions and notation for dealing with
programs and side-channels.

Shown in Figure~\ref{fig:side-channel-attack}. We assume a program ($\beta$) has $K$ as its sensitive input. $K$ should be 
a finite set of keys. The program also takes known messages $M$ as its input. 
During an AES encryption, for example, 
$\beta$ is the encryption function. $K$ is the set of all possible AES keys, 
and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have 
some observations ($O$) of the program. Examples of those observations include 
timing, CPU usages, and electromagnetic signals (EM). This paper only
uses secret-dependent control flows and secret-dependent data 
accesses as observations.

With the above definition, we have the following mapping between $\beta$,
$K$, $M$, and $O$:
%\vspace*{-0pt}
\begin{displaymath}
    \beta(K, M) \rightarrow O
\end{displaymath}

We model a side-channel in the following way. An adversary does not have
access to $K$, but he knows $\beta$, $M$, and $O$. For one execution of a
deterministic program, once $k \in K$ and $m \in M$ are fixed, the observation
($o \in O$) should also be determined. An attacker knows $\beta$, $o$,
and $m$. The attacker wants to infer the value of $k$. We use $K^o$ to denote
the set of possible $k$ values that produce the same observation: $K^o = \{ k \in K \, |\, \beta(k, m) \rightarrow o\}$
